A tutorial on the model-dependent analysis of neutron and X-ray reflectometry

### 2020-07-08 refl_maths/paper.tex
starting on resolution

>>>>

\section{Instrumental resolution}
In the analysis process, a resolution function associated with the instrumentation the reflectometry measurement was performed on it typically introduced to the model. 
This ensures greater accuracy in the modelled reflectometry to the experiment. 
These resolution functions are non-trival to define, however, the majority of reflectometry instruments will be able to offer information about the appropriate function to use.

Here, we will briefly discuss the introduction of a simple Gaussian resolution function of given width.
